\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{\articletitle}

### 2015-04-07 paper/paper.tex
paper updates
component

\subsection{Implementation}
The algorithm is divided into two subalgorithms. The subalgorithm \textit{gettwins} finds all twins and false twins and the subalgorithm \textit{preprocessing} replaces each (false) twin by a single colored vertex as described above. In the following subsections these algorithms and their worst case time complexities will be analyzed. The elementary operation is the comparison of two elements. In those subsections $n$ is the number of vertices of a graph $G(V,E)$ and $m$ is the number of edges of that graph.

>>>>

\subsection{Implementation}
The algorithm is divided into two subalgorithms. The subalgorithm \emph{gettwins} finds all twins and false twins and the subalgorithm \emph{preprocessing} replaces each (false) twin by a single colored vertex as described above. In the following subsections these algorithms and their worst case time complexities will be analyzed. The elementary operation is the comparison of two elements. In those subsections $n$ is the number of vertices of a graph $G(V,E)$ and $m$ is the number of edges of that graph.
